---
title: "Calculating rifle vs. rifle success rates"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Calculating rifle vs. rifle success rates}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r}
#| label: setup-knitr
#| include: FALSE
knitr::opts_chunk$set(
  collapse = TRUE,
  echo = TRUE,
  include = TRUE,
  warning = FALSE,
  message = FALSE,
  comment = "#>"
)
```

Let's try to replicate the results shown in the tweet below.

<blockquote class="twitter-tweet">

<p lang="en" dir="ltr">

Top 10 NA players at RIFLE vs. RIFLE fights in 2022 (phantom/vandal):<br><br>1. <a href="https://twitter.com/Cryocells_?ref_src=twsrc%5Etfw">@Cryocells_</a> (58%)<br>2. <a href="https://twitter.com/NiSMO_VAL?ref_src=twsrc%5Etfw">@NiSMO_VAL</a> (58%)<br>3. <a href="https://twitter.com/trentFPS?ref_src=twsrc%5Etfw">@trentFPS</a> (58%)<br>4. <a href="https://twitter.com/DerrekOW?ref_src=twsrc%5Etfw">@DerrekOW</a> (55%)<br>5. <a href="https://twitter.com/diceyzx?ref_src=twsrc%5Etfw">@diceyzx</a> (54%)<br>6. <a href="https://twitter.com/yay?ref_src=twsrc%5Etfw">@yay</a> (54%)<br>7. <a href="https://twitter.com/valyngod?ref_src=twsrc%5Etfw">@valyngod</a> (53%)<br>8. <a href="https://twitter.com/TenZOfficial?ref_src=twsrc%5Etfw">@TenZOfficial</a> (53%)<br>9. <a href="https://twitter.com/777eeiu?ref_src=twsrc%5Etfw">@777eeiu</a> (53%)<br>10. <a href="https://twitter.com/s0mcs?ref_src=twsrc%5Etfw">@s0mcs</a> (53%)<br><br>What surprises you?

</p>

--- Weltis (@WeltisGames) <a href="https://twitter.com/WeltisGames/status/1578931912516636672?ref_src=twsrc%5Etfw">October 9, 2022</a>

</blockquote>

```{=html}
<script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>
```
We start by identifying the events that he mentioned. (*"Data using Group Stages and Playoffs for VCT Stage 1, 2 and LCQ. International LANs not used (due to likely average tougher competition."*)

```{r}
#| label: setup
library(valorantr)
library(dplyr)
library(tidyr)
library(purrr)
```

```{r}
#| label: load events
events <- load_valorant("events")
events_na2022 <- events |> 
  inner_join(get_all_region_names(), by = "regionId") |> 
  filter(regionName == "North America" & !grepl("2021", name)) |> 
  distinct(event_id = id, event_name = name)
events_na2022
```

And then we grab all series played at those events.

```{r}
#| label: load series
series <- load_valorant("series")

series_na2022 <- series |> 
  rename(event_id = eventId, start_date = startDate) |> 
  inner_join(
    events_na2022,
    by = "event_id"
  ) |> 
  unnest_wider(c(team1, team2), names_sep = "_") |>
  select(
    series_id = id, 
    event_id, 
    team1_id,
    team1_name = team1_name,
    team2_id,
    team2_name = team2_name
  )
series_na2022
```

And all matches in those series.

```{r}
#| label: load matches
set_names_from_id_element <- function(x) {
  match_ids <- x |> map_int(~pluck(.x, "id"))
  x |> set_names(match_ids)
}
matches <- load_valorant("matches") |> set_names_from_id_element()
matches_na2022 <- matches[names(matches) %in% as.character(series_na2022$series_id)]
```

Before we move on, we should stop and make some helpful "mappings" for IDs for series, matches, players, and teams.

```{r}
#| label: prep mapping
series_player_mapping_na2022 <- matches_na2022 |> 
  map_dfr(
    ~pluck(.x, "playerStats"),
    .id = "series_id"
  ) |> 
  distinct(series_id, team_number = teamNumber, player_id = playerId) |> 
  mutate(across(series_id, as.integer))

map_pluck_matches <- function(matches, element) {
  matches |> map_int(~pluck(.x, element))
}

series_team_mapping_na2022 <- tibble(
  series_id = matches_na2022 |> map_pluck_matches("id"),
  `1` = matches_na2022 |> map_pluck_matches("team1Id"),
  `2` = matches_na2022 |> map_pluck_matches("team2Id")
) |> 
  pivot_longer(
    -series_id,
    names_to = "team_number",
    values_to = "team_id"
  ) |> 
  mutate(
    across(team_number, as.integer)
  )

series_team_player_mapping_na2022 <- series_player_mapping_na2022 |> 
  inner_join(
    series_team_mapping_na2022 |> 
      transmute(series_id, team_number, team_id), 
    by = c("series_id", "team_number")
  ) |> 
  select(-team_number)

series_match_mapping_na2022 <- matches_na2022 |> 
  map_dfr(
    ~tibble(match_id = pluck(.x, "matches", "id")), 
    .id = "series_id"
  ) |> 
  mutate(
    across(series_id, as.integer)
  )
```

Next, we grab the round details of all the matches, including round events and load-outs.

```{r}
#| label: load match details
## the names for matches are series ids
## the names for match details are match ids (individual maps between two teams)
match_details <- load_valorant("match_details") |> set_names_from_id_element()
match_details_na2022 <- match_details[names(match_details) %in% as.character(series_match_mapping_na2022$match_id)]
```

```{r}
#| label: load events and economies
cleanly_pluck_from_match_details <- function(match_details, element) {
  match_details |> 
    map_dfr(~pluck(.x, element), .id = "match_id") |> 
    as_tibble()
}

match_events_na2022 <- match_details_na2022 |> cleanly_pluck_from_match_details("events")
econ_na2022 <- match_details_na2022 |> cleanly_pluck_from_match_details("economies")
```

Then, we create a dataframe of weapon kills, combining the match details with the various mappings that we created before.

```{r}
#| label: weapon kills
players <- load_valorant("players")
teams <- get_all_team_names()
weapon_ids <- get_all_weapon_names() |>
  select(
    weapon_id = weaponId, 
    weapon = weaponName, 
    weapon_category = weaponCategory
  )

weapon_kills_na2022 <- match_events_na2022 |> 
  filter(!is.na(killId), damageType == "weapon") |> 
  transmute(
    across(match_id, as.integer),
    round_id = roundId,
    round_number = roundNumber,
    kill_id = killId,
    killer_id = playerId, 
    victim_id = referencePlayerId,
    killer_weapon_id = weaponId
  ) |> 
  ## data doesn"t list victim"s actual weapon, so we use what they bought in their loadout
  left_join(
    econ_na2022 |> 
      transmute(
        across(match_id, as.integer),
        round_id = roundId,
        victim_id = playerId, 
        victim_weapon_id = weaponId
      ),
    by = c("match_id", "round_id", "victim_id")
  ) |> 
  left_join(
    series_match_mapping_na2022,
    by = "match_id"
  ) |> 
  left_join(
    series_team_player_mapping_na2022 |> 
      select(
        series_id, 
        killer_id = player_id, 
        killer_team_id = team_id
      ),
    by = c("series_id", "killer_id")
  ) |> 
  left_join(
    series_team_player_mapping_na2022 |> 
      select(
        series_id, 
        victim_id = player_id, 
        victim_team_id = team_id
      ),
    by = c("series_id", "victim_id")
  ) |>
  left_join(
    players |> select(killer_id = id, killer_ign = ign),
    by = "killer_id"
  ) |> 
  left_join(
    players |> select(victim_id = id, victim_ign = ign),
    by = "victim_id"
  ) |> 
  left_join(
    teams |> select(killer_team_id = id, killer_team_name = name),
    by = "killer_team_id"
  ) |> 
  left_join(
    teams |> select(victim_team_id = id, victim_team_name = name),
    by = "victim_team_id"
  ) |> 
  left_join(
    weapon_ids |> rename_all(~sprintf("killer_%s", .x)),
    by = "killer_weapon_id"
  ) |> 
  left_join(
    weapon_ids |> rename_all(~sprintf("victim_%s", .x)),
    by = "victim_weapon_id"
  )
glimpse(weapon_kills_na2022)
```

Next, we count up how many kills and deaths individual players had in their Phantom/Vandal vs. Phantom/Vandal scenarios.

```{r}
rifle_rifle_win_rates_by_player_na2022 <- bind_rows(
  weapon_kills_na2022 |> 
    mutate(
      ign = killer_ign, 
      player_id = killer_id, 
      is_killer = TRUE
    ),
  weapon_kills_na2022 |> 
    mutate(
      ign = victim_ign, 
      player_id = victim_id,
      is_killer = FALSE
    )
) |> 
  ## could due ALL rifles for real for real
  # filter(
  #   killer_weapon_category == "rifle" &
  #   victim_weapon_category == "rifle"
  # ) |>
  filter(
    (killer_weapon %in% c("phantom", "vandal")) &
      (victim_weapon %in% c("phantom", "vandal"))
  ) |>
  count(player_id, ign, is_killer, sort = TRUE) |> 
  group_by(player_id, ign) |> 
  mutate(total = sum(n), prop = n / total) |> 
  ungroup() |> 
  filter(is_killer) |>
  select(-is_killer) |> 
  arrange(desc(prop))
rifle_rifle_win_rates_by_player_na2022
```

Before we look at the results, let's make one final mapping to link players to the last teams that they played with. This adds a bit of extra information for our final results.

```{r}
#| label: last_player_team_mapping_na2022
last_player_team_mapping_na2022 <- series_team_player_mapping_na2022 |> 
  group_by(player_id) |> 
  slice_max(series_id, n = 1, with_ties = FALSE) |> 
  ungroup() |> 
  select(player_id, team_id) |> 
  left_join(
    players |> select(player_id = id, ign),
    by = "player_id"
  ) |> 
  left_join(
    teams |> 
      select(team_id = id, last_team = name),
    by = "team_id"
  )
```

Finally, the results. (We use a minimum of 200 fights like Weltis.) The top 10 are very close to those that were posted.

```{r}
top_rifle_rifle_win_rates_na2022 <- rifle_rifle_win_rates_by_player_na2022 |> 
  filter(total >= 200) |> 
  inner_join(
    last_player_team_mapping_na2022 |> select(player_id, last_team),
    by = "player_id"
  ) |> 
  transmute(
    rank = row_number(desc(prop)),
    ign,
    last_team,
    n,
    total,
    prop
  )
top_rifle_rifle_win_rates_na2022 |> head(20)
```

Here's a direct comparison of our lists.

| Player | Weltis Rank | Weltis % | valorantr Rank | valorantr % |
|--------|------------:|---------:|---------------:|------------:|
| Cryo   |           1 |       58 |              1 |          57 |
| NiSMO  |           2 |       58 |              3 |          56 |
| trent  |           3 |       58 |              2 |          56 |
| Derrek |           4 |       55 |              8 |          54 |
| dicey  |           5 |       54 |              4 |          55 |
| yay    |           6 |       54 |             10 |          53 |
| valyn  |           7 |       53 |              6 |          55 |
| TenZ   |           8 |       53 |             14 |          53 |
| eeiu   |           9 |       53 |             27 |          51 |
| s0ms   |          10 |       53 |             21 |          51 |
