---
title: "Introduction to {valorantr}"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{valorantr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r}
#| label: setup-knitr
#| include: FALSE
knitr::opts_chunk$set(
  collapse = TRUE,
  echo = FALSE,
  include = TRUE,
  warning = FALSE,
  message = FALSE,
  comment = "#>"
)
```

`{valorantr}` makes it easy to retrieve data from rib.gg's API.

```{r}
#| label: setup
library(valorantr)
library(janitor)
library(dplyr)
library(tidyr)
library(purrr)
library(stringr)
```

## Events

We can retrieve tournaments (events) with a query string passed to `get_events`. If you're query string doesn't match something that the API recognized, a default set of results will be returned (determined by the API).

```{r}
#| label: get_events
vct_champs_events <- get_events('VALORANT Champions 2022')

vct_champs_playoffs_events <- vct_champs_events |> 
  filter(name == 'VALORANT Champions 2022 - Playoffs')
glimpse(vct_champs_playoffs_events)
```

## Series

We can retrieve all of the series played at an event with `get_series`.

```{r}
#| label: get_series
vct_champs_playoffs_series <- get_series(vct_champs_playoffs_events$id) |> 
  unnest_wider(c(team1, team2), names_sep = '_') |> 
  clean_names()
glimpse(vct_champs_playoffs_series)
```

We can filter for a specific series from the set of series.

```{r}
#| label: get_series
optic_liquid_series <- vct_champs_playoffs_series |> 
  filter(team1_short_name == 'OPTC', team2_short_name == 'TL')
glimpse(optic_liquid_series)
```

## Matches

We can retrieve all of the "maps" played in a series (most are best of three).

```{r}
#| label: get_matches
optic_liquid_matches <- get_matches(optic_liquid_series$id)
names(optic_liquid_matches) <- make_clean_names(names(optic_liquid_matches))
str(optic_liquid_matches, max.level = 1)
```

We can retrieve players involved in the series with `get_player`.

```{r}
#| label: get_player
optic_liquid_players <- optic_liquid_matches$player_stats |> 
  distinct(player_id = playerId) |> 
  mutate(
    data = map(player_id, get_player)
  )

optic_liquid_player_names <- optic_liquid_players |> 
  tidyr::hoist(
    data,
    "ign",
    "first_name" = "firstName",
    "last_name" = "lastName",
    "team_id" = list("team", "id"),
    "team_short_name" = list("team", "shortName")
  ) |>
  select(-data) |>
  mutate(
    across(c(first_name, last_name), stringr::str_squish)
  )
glimpse(optic_liquid_player_names)
```

## Match details

We can retrieve details of a match (best-of-25 rounds).

```{r}
#| label: get_match_details
optic_liquid_match_details <- optic_liquid_matches$matches$id |> 
  set_names() |> 
  map(get_match_details)
str(optic_liquid_match_details, max.level = 2)
```

One of the interesting results is x-y coordinates of players.

```{r}
#| label: get_match_locations
optic_liquid_match_details_m3 <- optic_liquid_match_details$`79018`
glimpse(optic_liquid_match_details_m3$locations)
```
