---
title: "Introduction to {valorantr}"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{valorantr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r}
#| label: setup-knitr
#| include: FALSE
knitr::opts_chunk$set(
  collapse = TRUE,
  echo = TRUE,
  include = TRUE,
  warning = FALSE,
  message = FALSE,
  comment = "#>"
)
```

`{valorantr}` makes it easy to retrieve data from [rib.gg](https://rib.gg)'s API.

```{r}
#| label: setup
library(valorantr)
library(janitor)
library(dplyr)
library(tidyr)
library(purrr)
```

## Events

We can retrieve tournaments (events) with a query string passed to `get_events`. If you're query string doesn't match something that the API recognized, a default set of results will be returned (determined by the API).

```{r}
#| label: get_events
vct_champs_events <- get_events("VALORANT Champions 2022")

vct_champs_playoffs_events <- vct_champs_events |> 
  filter(name == "VALORANT Champions 2022 - Playoffs")
glimpse(vct_champs_playoffs_events)
```

We can load pre-saved events saved in the `events` release in `valorant-data` with `load_valorant("events)`.

```{r}
#| label: presaved_events
presaved_events <- load_valorant("events")
nrow(presaved_events)
```

```{r}
#| label: presaved_vct_champs_playoffs_events
presaved_events |> 
  filter(id == vct_champs_playoffs_events$id) |> 
  glimpse()
```

See all of the releases that can be read with `load_valorant()` [here](https://github.com/tonyelhabr/valorant-data/blob/master/README.md).

Some ID fields in the returned data may not be obvious. For example, what is `regionId = 7`? There are various `get_all_{x}_names()` functions written to help with ID-name mappings. In this case, `get_all_region_names()` is helpful.

```{r}
#| label: get_region_ids
get_all_region_names()
```

## Series

We can retrieve all of the series played at an event with `get_series`.

```{r}
#| label: get_series
cleanly_unnest_series <- function(series) {
  series |> 
    unnest_wider(c(team1, team2), names_sep = "_") |> 
    clean_names()
}

vct_champs_playoffs_series <- get_series(vct_champs_playoffs_events$id) |> 
  cleanly_unnest_series()
glimpse(vct_champs_playoffs_series)
```

We can filter for a specific series from the set of series.

```{r}
#| label: optic_liquid_series
optic_liquid_series <- vct_champs_playoffs_series |> 
  filter(team1_short_name == "OPTC", team2_short_name == "TL")
glimpse(optic_liquid_series)
```

We can use `get_all_map_names()` to identify which maps are played in the series.

```{r}
#| label: get_all_map_names
optic_liquid_series |> 
  hoist(
    matches,
    matchId = 'id',
    mapId = 'mapId'
  ) |> 
  select(seriesId = id, matchId, mapId) |> 
  unnest_longer(c(matchId, mapId)) |> 
  inner_join(
    get_all_map_names(),
    by = 'mapId'
  )
```

We can load pre-saved series with `load_valorant("series")`.

```{r}
#| label: presaved_series
presaved_series <- load_valorant("series")
nrow(presaved_series)
```

```{r}
#| label: presaved_optic_liquid_series
presaved_series |> 
  filter(id == optic_liquid_series$id) |> 
  cleanly_unnest_series() |> 
  glimpse()
```

## Matches

We can retrieve all of the "maps" played in a series (most are best of three).

```{r}
#| label: get_matches
optic_liquid_matches <- get_matches(optic_liquid_series$id)
names(optic_liquid_matches) <- make_clean_names(names(optic_liquid_matches))
str(optic_liquid_matches, max.level = 1)
```

We can load pre-saved matches with `load_valorant("matches")`.

```{r}
#| label: presaved_matches
presaved_matches <- load_valorant("matches")
length(presaved_matches)
```

```{r}
#| label: presaved_optic_liquid_matches
set_names_from_id_element <- function(x) {
  match_ids <- x |> map_int(~pluck(.x, "id"))
  x |> set_names(match_ids)
}
presaved_matches <- set_names_from_id_element(presaved_matches)

presaved_matches[[as.character(optic_liquid_matches$id)]] |> 
  str(max.level = 1)
```

## Players

We can retrieve players involved in the series with `get_player`.

```{r}
#| label: get_player
optic_liquid_players <- optic_liquid_matches$player_stats |> 
  distinct(player_id = playerId) |> 
  pull(player_id) |> 
  map_dfr(get_player)
glimpse(optic_liquid_players)
```

We can load pre-saved players with `load_valorant("players")`.

```{r}
#| label: presaved_players
presaved_players <- load_valorant("players")
nrow(presaved_players)
```

```{r}
#| label: presaved_optic_liquid_player_names
presaved_players |> 
  filter(id %in% optic_liquid_players$id) |> 
  glimpse()
```

## Match details

We can retrieve details of a match (best-of-25 rounds).

```{r}
#| label: get_match_details
optic_liquid_match_details <- optic_liquid_matches$matches$id |> 
  map(get_match_details)
str(optic_liquid_match_details, max.level = 2)
```

One of the interesting results is x-y coordinates of players.

```{r}
#| label: get_match_locations
optic_liquid_match_details_m3 <- optic_liquid_match_details[[3]]
glimpse(optic_liquid_match_details_m3$locations)
```

We can load pre-saved match details with `load_valorant("match_details")`.

```{r}
#| label: presaved_match_details
presaved_match_details <- load_valorant("match_details")
length(presaved_match_details)
```

```{r}
#| label: presaved_optic_liquid_match_details_m3
presaved_match_details <- set_names_from_id_element(presaved_match_details)
presaved_optic_liquid_match_details_m3 <- presaved_match_details[[as.character(optic_liquid_match_details_m3$id)]]
presaved_optic_liquid_match_details_m3 |> str(max.level = 1)
```

We can use `get_all_weapon_names()`, `get_all_agent_names()`, `get_all_role_names()`, and `get_all_armor_names()` to augment the ID columns. Note that `get_all_agent_names()`, in addition to returning `agentId` and `agentName`, also returns `roleId`. (There is a 1-to-many mapping of agents to roles.)

```{r}
#| label: get_all_x_names
presaved_optic_liquid_match_details_m3$economies |> 
  select(roundId, roundNumber, playerId, weaponId, agentId, armorId) |> 
  inner_join(get_all_weapon_names(), by = "weaponId") |> 
  inner_join(get_all_agent_names(), by = "agentId") |> 
  inner_join(get_all_role_names(), by = "roleId") |> 
  inner_join(get_all_armor_names(), by = "armorId")
```
